### 2025-06-01 conteudo/introduction/intro.tex
add updated linux information

Maintaining the Linux kernel is a complex task, as the project contains more
than 19 million lines of code and has had over thirteen thousand contributors
throughout its lifespan \citep{linuxquantity}. Given the magnitude of the Linux
kernel project, it is unrealistic to expect that all contributors have
consistently followed the best programming practices and principles in every
contribution made to the project. Consequently, it is expected that a
significant amount of low-quality code artifacts will be found in the source
code, which could hinder or compromise the maintenance of the project and the
addition of new features.

@@

\todo[inline]{Require updated information about the linux kernel. Required from qualification exam.}

>>>>

Maintaining the Linux kernel is a complex task, as the project contains more
than 28 million lines of code and has had over twenty thousand contributors
throughout its lifespan
\footnote{Data directly extracted from Linux github repository \citep{linuxrepo}.
Counted  28783390 lines of code and 20699 number of contributors in May 29th, 2025.
Number of contributors counted as number of unique full name listed as author of a patch.}.
Given the magnitude of the Linux
kernel project, it is unrealistic to expect that all contributors have
consistently followed the best programming practices and principles in every
contribution made to the project. Consequently, it is expected that a
significant amount of low-quality code artifacts will be found in the source
code, which could hinder or compromise the maintenance of the project and the
addition of new features.

@@
